Binarity's Biases on Transit Survey Occurrence Rates

### 2018-02-28 paper/main.tex
tex cleanup

To compute the apparent occurrence rate density, we need to make
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different.  For a given value of $r\a$, the
  number of binary systems in the searchable sample with mass ratio
  $(q, q+\mathrm{d}q)$ is
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\, {n_{\rm b}\over n_{\rm s}}
    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Equation~\ref{eq:N_binaries} replaces ${\mu N_\star(r\a)/(1+\mu)}$
in Equations~\ref{eq:n1} and~\ref{eq:n2}.
The whole equation is then integrated to give the number of
detected planets.

@@

Taking these modifications into account, a general formula for the
apparent rate density is
\begin{align}
    \notag
    \Gamma\a(r\a) &= \frac{1}{1+\mu} \,
    \left\{ \Gamma_0(r\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a)\cdot
         \frac{R(qM)}{R(M)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
%The \hyperref[sec:appendix]{appendix} gives a more formal derivation
%of this equation.
We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
distribution for binaries contained within the searchable sample of
sources.  With this in mind we may rewrite
Equation~\ref{eq:general_Gamma_a} as
\begin{align}
    %\notag
    %\notag
    \Gamma\a(r\a)
    =%&= 
    {1\over 1+\mu} \,
    \left[
       \Gamma_0(r\a)%\phantom{\tilde \Gamma}\right.%&\\
       %&\left.
       +\mu\,
       \left\langle
       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a\right)
       +
       {\mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
       \cdot
       {R(qM) \over R(M)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over all the binaries in the
searchable sample.

@@

%Of course, effects unrelated to
%binarity would also ``blur'' the gap in the planet radius dimension.
%In particular, the valley's period-dependence is almost certainly not
%flat \citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
%means that any study measuring the gap's width or depth while
%accounting for binarity must either perform tests at fixed orbital
%period, or else marginalize over period and account for the associated
%blurring in the planet radius dimension.

@@

\begin{comment}
% JNW: These 2 sections do not seem very interesting.
  {\paragraph{Fraction of detected planets with binary companions}
A related effect is that some detected planets are more likely to be
in binary systems than others.  Notably, Figure~\ref{fig:frac_model_3}
predicts that the fraction of detected planets with binary companions
should increase by $6$~to~$12\%$ going from $2R_\oplus$ to
$1.4R_\oplus$.

In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
survey, they reported the fraction of planet-hosting stars with
Robo-AO detected companion stars, binned over apparent planet radii.
The fraction of KOIs with nearby stars and their $1\sigma$
uncertainties are:
\begin{itemize}
    \item Earths ($r\a < 1.6R_\oplus$): $16.3 \pm 1.0\%$, from 1480
    systems.
    \item Neptunes ($1.6R_\oplus < r\a < 3.9 R_\oplus$): $13.0 \pm
    0.8\%$, from 2058 systems.
    \item Saturns ($3.9R_\oplus < r\a < 9 R_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
    \item Jupiters ($r\a > 9R_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
\end{itemize} 
The uncertainties were calculated
following~\citet{burgasser_binarity_2003}.  The absolute values of the
companion fractions are lower than in the solar neighborhood at
least in part because of Robo-AO's sensitivity
(\citealt{ziegler_robo-ao_2017}'s
Figure~2;~\citealt{raghavan_survey_2010}).
%Another reason for the lower measured companion fraction could be
%that planetary systems are more rare in binary systems,
%as~\citealt{kraus_impact_2016} found for close binary companions).
The uptick in the companion rate for Jupiters is likely tied to a
large astrophysical false positive rate~\citep{santerne_sophie_2012}.
Going from Neptunes to Earths, the data suggest a weak increase in the
detected planet companion fraction, perhaps of a few percent.  It will
be interesting to see whether this effect is borne out by further
observations.}

\paragraph{Connection between high-resolution imaging and occurrence rates}

Occurrence rate calculations are beginning to incorporate the results
of high-resolution imaging surveys.  For example, recent studies have
reduced contamination in the numerator of the occurrence rate by
using~\citet{furlan_kepler_2017}'s catalog to test the effects of
removing KOI hosts with known companions
(\citealt{fulton_california-_2017}; \citealt{petigura_CKS_2017}).
This is a good first step, but the denominator remains uncorrected.

Even if the multiplicity of every star that {\it Kepler} surveyed were
known, the problem would not be solved. In this scenario, it would be
possible to tabulate planet occurrence for single and binary star
systems separately.  The number of planets per single star would
be known.  However the number of planets per primary and secondary
would still be convolved.  An observational approach to separating the
two populations might be to analyze the centroids, or the transit
durations (and thus host star densities) for a representative sample
of planets in binary systems.

A theory-driven solution might entail probabilistic population
inference, with a parametrized model for planet populations around
primary and secondary stars.  Such an approach might be expected to
find that the primary and secondary populations are different, since
single M dwarfs host more small planets than FGK
dwarfs~\citep{dressing_occurrence_2015}.  Given the difficulty of
writing a likelihood function in a survey with systematic
biases, one possible approach might be to forward-model the survey in
the framework of approximate Bayesian
computation~\citep[\textit{e.g.},][]{morehead_understanding_2016}.

\end{comment}

\begin{comment}
%LB: the below paragraph seems like it is just making caveats for no
%good reason. We've been explicit throughout that we have a
%restrictive set of assumptions...

  \paragraph{Practical effects: smooth detection efficiencies and finite SNR floors}
  To apply this study to real transit surveys, a few practical concerns
  become pressing.  One issue is that space-based missions with
  telemetric requirements often must select target stars.  Even if the
  selection process aims to create an SNR-limited survey,
  as~\citet{batalha_selection_2010} did for {\it Kepler}, uncertainties
  in stellar parameters and the modeled instrument performance can lead
  to deviations away from an SNR-limited stellar sample.

  Another concern is that in real transit surveys the detection
  efficiency is not a step function in SNR.  Transit survey pipeline
  detection efficiencies are usually smooth
  functions~\citep{christiansen_measuring_2016,fulton_california-_2017}.
  If we were to assume a smooth detection probability in SNR, we would
  need to appropriately weight our occurrence calculation for planets
  with low probabilities of being detected.

  The simplest way to avoid the conceptual complications of accounting
  for finite detection efficiency is to raise the SNR floor, to {\it
  e.g.,} ${\rm SNR} \approx 12$ for {\it Kepler}
  (\citealt{fulton_california-_2017}, Figure~5).  To a good
  approximation, this allows use of the boolean distinctions
  ``searchable'' and ``not searchable'' for signals of an observed depth
  (at fixed orbital period).  By making the survey strictly SNR-limited,
  rather than ``fuzzily SNR-limited'', the effects of unrecognized
  binaries become much easier to model.  Since the minimum SNR for
  detection is set arbitrarily\footnote{For example,
  {\it Kepler}'s threshold of ${\rm SNR}=7.1$ was set for there to be no
  more than one statistical false alarm across the full {\it Kepler}
  campaign~\citep{jenkins_tests_2002}. Equally valid would have been to
  insist on no more than $10^{-3}$ false alarms per survey, raising the
  detection floor.  }, this simplification would put occurrence rate
  studies on clearer conceptual ground, and facilitate the process of
  converting the apparent radius distributions into true radius
  distributions.

  Finally, our calculations ignored the fact that a transit survey's
  finite SNR floor could censor the apparent rate density. This would
  make planets with smaller apparent radii harder to detect.  Other than
  moving the small radii regime out of reach for that particular survey,
  this would not change any of our findings.

\end{comment}

\begin{comment}
%LB: the following are paragraphs from earlier discussion iterations

  To count the number of stars that
  were searched, further effort to understand the multiplicity
  statistics of KOI vs.~non-KOI stars is necessary. In particular, a
  non-KOI star high-resolution imaging effort could help estimate the
  systematic errors incurred by assuming all surveyed stars are single.
  An alternate approach would be to combine {\it Gaia} parallaxes with
  measured photometric fluxes and identify binary systems as those that
  are overluminous~\citep[\textit{e.g.},][]{widmark_inferring_2018}.

  \citet{ciardi_understanding_2015} studied the effects of stellar
  multiplicity on the planet radii derived from transit surveys.  They
  modeled the problem for {\it Kepler}\ objects of interest by
  matching a population of binary and tertiary companions to KOI
  stars, under the assumption that the KIC-listed stars were the
  primaries.  They then computed planet radius correction factors
  assuming that {\it Kepler}-detected planets orbited the primary or
  companion stars with equal probability (their Section~5).  Under
  these assumptions, they found that any given planet's radius is on
  average underestimated by a multiplicative factor of $\approx\!
  1.5$.  \citet{ziegler_robo-ao_2017} recently reported a similar mean
  radius correction factor for the multiple systems observed by the
  Robo-AO KOI survey, using the same assumption that detected planets
  are as likely to orbit the primary and the secondary.

  Of course, our model's assumptions (see the list in
  Section~\ref{sec:conclusion}) might not apply to the {\it Kepler}\
  dataset.  However if they are applicable, then for the $56\%$ of
  ``\texttt{CONFIRMED}'' KOIs\footnote{Exoplanet Archive;
  \cite{akeson_nasa_2013}; \url{exoplanetarchive.ipac.caltech.edu}} with
  apparent radii $>2r_\oplus$, whenever high-resolution imaging
  discovers a binary companion in a system that hosts a detected
  transiting planet, the planet is much more likely to orbit the
  primary.

  \paragraph{Independent approaches for estimating binarity's effects}
  T. Barclay et al.\! (in preparation) have performed the exercise of
  taking stars selected by the {\it Kepler}\ team, pairing them with a
  population of secondaries, injecting a realistic distribution of
  planet radii, and then comparing the inferred occurrence rates with
  the true ones.  In their model, they find that binarity leads to an
  inferred rate of Earth-sized planets $\approx 10\%$ less than the
  true rate.  In our Model \#3, if all $Z_i$'s are equal (a plausible
  assumption in the lack of evidence to the contrary), the
  underestimate is by a comparable 16\%.
\end{comment}

\begin{comment}
\section{Conclusion}
% JNW: Material seems redundant.
  This study presented a framework for estimating the impact of
unresolved binaries on transit survey occurrence rates. From
the order-of-magnitude argument presented in
Section~\ref{sec:simplest}, we showed that for Sun-like stars in the
local neighborhood, typical twin binary fractions yield apparent
occurrence rates that are well within a factor of two of the true
rates for single stars.

We then derived a general formula for the apparent rate density
inferred by observers who ignore binarity
(Equation~\ref{eq:general_Gamma_a}).  As input, this equation requires
a volume-limited mass ratio distribution, and the true rate densities
for planets around singles, primaries, and secondaries.  The
assumptions that enable this approach are as follows.
\begin{enumerate}
    \item The transit survey is SNR-limited
        (Equation~\ref{eq:S_N_thresh}).
    \item The observers know the true properties of the single
        and primary stars, and assign all unresolved binaries the
        properties of the primary.
    \item There are two functions, $L(M)$ and $R(M)$, that specify a
        star's luminosity and radius in terms of its mass.
\end{enumerate}

The interpretation of Equation~\ref{eq:general_Gamma_a} is that the
apparent rate density is a weighted sum of the rate densities for
single, primary, and secondary stars. The weights depend on the
relative numbers of binary and single stars in the searchable volumes,
which are affected by both dilution of transit signals and a Malmquist
bias.  Both effects should be considered in Monte Carlo simulations of
transit surveys~\citep[\textit{e.g.},][]{
  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.

Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
\begin{itemize}
%
\item If single, primary, and secondary stars all host the same number
  of planets per star, and the planet radius distribution is a power
    law with the exponent reported by~\citet{howard_planet_2012}, then
    binarity influences apparent planet occurrence rates at the few
    percent level. This applies for apparent radii from $2R_\oplus$ to
    $17R_\oplus$ (Section~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with the
  \citet{howard_planet_2012} exponent above $2R_\oplus$ and a constant
    occurrence below $2R_\oplus$, the rate density for radii below
    $2R_\oplus$ is overestimated. The magnitude of the error, $\Delta
    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
    smaller than current systematic uncertainties on the occurrence
    rates of Earth-sized planets, this implies that binarity could
    eventually become an important component of the $\eta_\oplus$
    error budget.
%
\item Binarity blurs sharp features in the radius distribution
  (Figure~\ref{fig:model_4}), to a degree that could affect precise
    measurements of the depth, width, and slope of
    the~\citet{fulton_california-_2017} radius gap.
    %in the event that
    %planets are not carefully vetted with high-resolution imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates
  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
    radius distribution, similar to that reported
    by~\citet{petigura_CKS_2017}.
%
\item Detected planets with apparent radii greater than $0.5R_\oplus$
  that are revealed by high-resolution imaging surveys to exist in
    binaries are more likely to orbit the primary
    (Figure~\ref{fig:frac_model_3}).
%
\item Near the break in occurrence as a function of planet
  radius at $2R_\oplus$, the fraction of detected planets with
    binary companions should increase by roughly $5$~to~$10\%$
    (Figure~\ref{fig:frac_model_3}).
\end{itemize}

These results are only strictly applicable for idealized transit
surveys meeting the criteria mentioned above.  For real transit
surveys, although our approach is only suggestive, we hope that it
provides a useful estimate for the systematic errors that can be
incurred by ignoring binarity in calculations of planetary occurrence
rates.
\end{comment}

@@

\newpage

\begin{comment}
\appendix
\section{Alternative derivation of apparent rate density}
\label{sec:appendix}

Here we present a more formal derivation of
Equation~\ref{eq:general_Gamma_a}.  We also generalize a bit further,
by allowing the occurrence rate density to depend on stellar mass $M$
as well as planet radius $r$.  We begin by writing the apparent rate
density $\Gamma\a$ as (in analogy to
Equation~\ref{eq:occ_rate_simple})
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \, \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}(r\a,M\a)$ is the number of detected planets per
star with radius $r\a$ orbiting stars of apparent mass $M\a$, per unit
$r\a$ and $M\a$.  This collection of planets with the same apparent
properties actually includes planets with a variety of true sizes and
host star masses.  We may write $n_{\rm det}(r\a, M\a)$ as the
convolution of the true occurrence rate density, $\Gamma(r, M)$; and
$\mathcal{N}_\star(r\a, M\a; r, M)$, the number of searchable stars
per unit $(r\a, M\a)$ for which a planet with true properties $(r, M)$
would appear to be a planet with apparent properties $(r\a, M\a)$:
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_{i=0}^2 n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_{i=0}^2 \int \mathrm{d}r \!\int\! \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \,\Gamma_i(r,M) \, p_{\rm tra}(M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the true type of host star, with 0 for single
stars, 1 for primary stars, and 2 for secondary stars.  We now proceed
to calculate $\mathcal{N}_\star^i(r\a,M\a; r,M)$.

\paragraph{Single stars}
For single stars,
\begin{equation}
    \mathcal{N}_\star^0(r\a,M\a; r,M)
    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
\end{equation}
where $\hat{\delta}$ is the Dirac delta function.
%Therefore,
%\begin{equation}
%    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
%    M\a) \, p_{\rm tra}(r\a, M\a).
%\end{equation}

\paragraph{Primary stars}
For primary stars in binary systems, 
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int_0^1 
      \mathrm{d}q\,f(q)\,\mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the binary mass ratio distribution in a volume-limited sample
of stars.  Since we are assuming that the observer will perceive a binary to be a single
star with the same properties as the primary star,
\begin{equation}
    \mathcal{N}_{\star,q}^1(r\a, M\a, q; r, M)
    \propto
    \hat{\delta}(M\a-M).
\end{equation}
In this case, $\mathcal{N}_{\star,q}^1$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, and the observed transit depth is
\begin{equation}
    \delta
    = \left({r\over R(M\a)}\right)^2\, {L(M\a) \over L_{\rm tot}(M\a, q)}
    \equiv \left[{r\over R(M\a)}\right]^2\, 
    \frac{1}{\mathcal{D}_1^2}
    \label{eq:delta_obs_primaries} 
\end{equation}
where
\begin{equation}
    L_{\rm tot}(M\a,q) = L(M\a) + L(qM\a),~~\mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
\end{equation}
The normalization of $\mathcal{N}_{\star,q}^1$ is given by the
number of binaries that are searchable for a signal $\delta$
and that have mass ratio $q$:
\begin{equation}
    N_\star^0(r\a, M\a)\,
    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
    \label{eq:primary_normalization}
\end{equation}
%where the argument for the number of searchable single stars,
%$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
Applying the preceding arguments, we find
\begin{align}
    \mathcal{N}_{\star, q}^1(r\a, M\a, q; r, M)
    &=N_\star^0(r\a, M\a)
    \, {n\b\over n\s} \, \mathcal{D}_1^3
    \,\hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_1}\right)\hat{\delta}(M\a-M).
    \label{eq:N_s_1}
\end{align}

\paragraph{Secondary stars}
In this case, $M=qM_1=qM\a$, so
\begin{equation}
    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
    \propto \hat{\delta}\left(M\a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_\star^2$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, but this time
\begin{equation}
      \delta =
      \left[{r\over R(qM\a)}\right]^2 \,
      {L(qM\a) \over L_{\rm tot}(M\a, q)}
      \equiv
      \left[{r\over R(M\a)}\right]^2\,
      \frac{1}{\mathcal{D}_2^2},
\end{equation}
where
\begin{equation}
  \mathcal{D}_2
  =
  \frac{R(qM\a)}{R(M\a)}
  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
\end{equation}
The normalization remains the same as the previous case~--~we are
counting the searchable stars at a given observed depth $\delta$, and
the total luminosity of the binary is the same.  Thus,
\begin{equation}
    \mathcal{N}_\star^2(r\a, M\a; r, M)
    =\int_0^1 \mathrm{d}q~f(q)\,\mathcal{N}_{\star, q}^2(r\a, M\a, q; r, M),
\end{equation}
where
\begin{align}
    \mathcal{N}_{\star,q}^2(r\a, M\a, q; r, M)
    =N_\star^0(r\a, M\a) \, \frac{n\b}{n\s} 
    \, \mathcal{D}_1^3
    \, \hat{\delta} \left(r\a-\frac{r}{\mathcal{D}_2}\right)
    \hat{\delta} \left(M\a-{M\over q}\right).
    \label{eq:mathcal_N_s_2}
\end{align}

\paragraph{Number of detected planets}
Inserting the results into Equation~\ref{eq:n_det}, we find
\begin{align}
    \notag
    n_{\rm det}^0(r\a, M\a)
    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^0(r\a, M\a; r, M)
    \, \Gamma_0(r, M) \, p_{\rm tra}(M)\\
    &=N_\star^0(r\a, M\a)\, \Gamma_0(r\a, M\a) \, p_{\rm 
        tra}(M\a),
    \label{eq:n_det_0}
    \\
    \notag
    n_{\rm det}^1(r\a, M\a)
    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^1(r\a, M\a; r, M)
    \, \Gamma_1(r, M) \, p_{\rm tra}(M)\\
    &=N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \,
    \frac{n\b}{n\s}
    \int \mathrm{d}q \,
         \mathcal{D}_1^3 f(q)\cdot
         \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a),\\
    n_{\rm det}^2(r\a, M\a)
    \notag
    &=\int\mathrm{d}r\,\mathrm{d}M~\mathcal{N}_\star^2(r\a, M\a; r, M)
    \, \Gamma_2(r, M) \, p_{\rm tra}(M)\\
    &=
    N_\star^0(r\a, M\a)\, p_{\rm tra}(M\a) \, \frac{n\b}{n\s}
    \int {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
         \frac{R(qM\a)}{R(M\a)} q^{-1/3}.
    \label{eq:n_det_2}
\end{align}

Finally, combining these results, the
apparent occurrence rate density
\begin{align}
    \Gamma\a(r\a,M\a) &= 
    \frac{1}{N_\star(r\a,M\a) p_{\rm tra}(r\a,M\a)} \,
    \sum_{i=0}^2 n_{\rm det}^i (r\a,M\a)
\end{align}
becomes
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu} \,
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
    \right] \right\}.
\end{align}
%We validate this equation in limits where it is possible to write down
%the answer (e.g., Equation~\ref{eq:formula_twin_binary}), and also
%against a Monte Carlo realization of the twin binary models
%(Sections~\ref{sec:model_1} and~\ref{sec:model_2}).
\end{comment}

>>>>

To compute the apparent occurrence rate density, we need to make
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different.  For a given value of $r\a$, the
  number of binary systems in the searchable sample with mass ratio
  $(q, q+\mathrm{d}q)$ is
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\, {n_{\rm b}\over n_{\rm s}}
    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Equation~\ref{eq:N_binaries} replaces ${\mu N_\star(r\a)/(1+\mu)}$
in Equations~\ref{eq:n1} and~\ref{eq:n2}.
The whole equation is then integrated to give the number of
detected planets.

@@

Taking these modifications into account, a general formula for the
apparent rate density is
\begin{align}
    \notag
    \Gamma\a(r\a) &= \frac{1}{1+\mu} \,
    \left\{ \Gamma_0(r\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a)\cdot
         \frac{R(qM)}{R(M)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
distribution for binaries contained within the searchable sample of
sources.  With this in mind we may rewrite
Equation~\ref{eq:general_Gamma_a} as
\begin{align}
    \Gamma\a(r\a)
    =
    {1\over 1+\mu} \,
    \left[
       \Gamma_0(r\a)
       +\mu\,
       \left\langle
       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a\right)
       +
       {\mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
       \cdot
       {R(qM) \over R(M)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over all the binaries in the
searchable sample.

@@

%Of course, effects unrelated to binarity would also ``blur'' the gap
%in the planet radius dimension.  In particular, the valley's
%period-dependence is almost certainly not flat
%\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.  This
%means that any study measuring the gap's width or depth while
%accounting for binarity must either perform tests at fixed orbital
%period, or else marginalize over period and account for the
%associated blurring in the planet radius dimension.

@@

@@
